Lawvere-Tierney Sheafification\\ in Homotopy Type Theory

### 2015-01-18 paper/sheaf_lics.tex
improve code a little bit / Explain admits from equality of diagrams
Summary+ admits not solved

\begin{prop}
  A left exact modality $\modal$ induces a consistent type theory if
  and only if $\modal \zero$ can not be inhabited in the initial type
  theory. In that case, the modality is said to be consistent.
\end{prop}
\begin{proof}
  By condition (iv) of Definition~\ref{sec:defin-basic-prop-1},
  $\modal \zero$ is an initial object of $\Type^\modal_p$, and thus
  corresponds to false for modal mere proposition.
  % 
  As $\modal \one = \one$, $\Type^\modal_p$ is consistent when
  $\modal \zero \neq \one$, that is when there is no proof of
  $\modal \zero$.
\end{proof}

@@

Using the same idea of proof as in proposition~\ref{prop:sep-mod}, we have
\begin{prop}
  $(\modal_{n+1},\nu)$ defines a reflective subuniverse.
\end{prop}

@@

@@

In our formalization of sheafification defined
Section~\ref{sec:sheafification} (done in 
\texttt{sheaf\_induction.v}), five very technical facts required to
show that $\square$ and $\modal_{n+1}$ are modalities have been
admitted. Nevertheless, we are confident that they can be proven and
have been admitted only by lack of time.

>>>>

\begin{prop}\label{prop:consistent}
  A left exact modality $\modal$ induces a consistent type theory if
  and only if $\modal \zero$ can not be inhabited in the initial type
  theory. In that case, the modality is said to be consistent.
\end{prop}
\begin{proof}
  By condition (iv) of Definition~\ref{sec:defin-basic-prop-1},
  $\modal \zero$ is an initial object of $\Type^\modal_p$, and thus
  corresponds to false for modal mere proposition.
  % 
  As $\modal \one = \one$, $\Type^\modal_p$ is consistent when
  $\modal \zero \neq \one$, that is when there is no proof of
  $\modal \zero$.
\end{proof}

@@

Using the same idea of proof as in proposition~\ref{prop:sep-mod}, we have
\begin{prop}
  $(\modal_{n+1},\nu)$ defines a modality.
\end{prop}

@@

Starting from any left-exact modality $\modal_{-1}$ on $\HProp$, we
defined in this paper a new left-exact modality $\modal$ on
$\sum_{T:\Type} \sum_{n} \IsType n T$, which is exactly $\modal_{-1}$
when restricted to $\HProp$.

If $\modal_{-1}$ is the double negation modality on $\HProp$, it is obvious
that $\modal_{-1}\zero=\zero$, hence the homotopy type theory induced by
$\modal$ is consistent by proposition~\ref{prop:consistent}.

In topos theory, the topos of Lawvere-Tierney sheaves for the double
negation topology is a boolean topos. In homotopy type theory, this
result can be expressed as:

\begin{prop}
  If $\modal_{-1}=\modal_{\lnot\lnot}$, and $\modal$ is the modality
  as defined above, then the propositional excluded middle is true in
  the induced type theory.
\end{prop}

@@

In our formalization of sheafification defined
Section~\ref{sec:sheafification} (done in 
\texttt{sheaf\_induction.v}), three very technical facts required to
show that $\square$ and $\modal_{n+1}$ are modalities have been
admitted. Nevertheless, we are confident that they can be proven and
have been admitted only by lack of time.
In the proof that diagrams are equal in lemma~\ref{lem:sepiscolim},
the equality of projections is admitted, because if this proof is
obvious on paper, it becomes really technical when formalized.
As a consequence, the fact that $P$ is a colimit of the diagonal
closed diagram is admitted too, but again, this proof should be really
short as it is on paper.
